The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-21 draft/ms.tex
24 Jup mass criteria

The scope of the EOD has expanded, and there are two major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only had
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also have planets discovered via timing. For the
future, exoplanets discovered by any other methods with robust
detections and good orbital parameters will also be included in the
EOD.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to be smaller than (ZZZ change to mass
ratio) 24 \mjup\ and to have robust detections and well-determined
orbits (though these are not strictly quantitative; see Section~2 of
\citealt{Wright2011}). When new evidence comes to light and we are no
longer confident about the planet, we remove it from EOD, even if the
evidence is not peer reviewed.

>>>>

The scope of the EOD has expanded, and there are three major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only had
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also have planets discovered via timing. For the future, exoplanets discovered by any other methods with robust detections and good orbital parameters will also be included in the
EOD. Previously, we required the planets to be smaller than 24 \mjup\ but now we require the mass ratio to be smaller than 24 \mjup$/\msun$.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to have robust detections and well-determined
orbits (though these are not strictly quantitative; see Section~2 of
\citealt{Wright2011}). When new evidence comes to light and we are no
longer confident about the planet, we remove it from EOD, even if the
evidence is not peer reviewed.
